### 2023-12-30 talk/aprm24.tex
edits to aprm24

\begin{frame}{Questions to be addressed}

  \begin{enumerate}
  \item When can we carry out full-information likelihood-based inference on a general class of spatiotemporal partially observed Markov process models? In particular, models for networks of interacting biological population dynamics.

@@

  \item Is there an intersection between scientific problems of interest and the capabilities of the \texttt{spatPomp} R package?

\item We introduce the {\bf iterated block particle filter}, currently the most powerful algorithm available in \texttt{spatPomp}.

\item Bonus question: How do we know if our model is statistically adequate, or needs more work?

@@

\begin{frame}{Practical inference using IBPF}
  \bi
  \item to do

@@

>>>>

\begin{frame}{Question to be addressed}

  \begin{enumerate}
  \item When can we carry out full-information likelihood-based inference on nonlinear non-Gaussian spatiotemporal partially observed Markov process (SpatPOMP) models? In particular, models for networks of interacting biological population dynamics.

@@

\item We introduce the {\bf iterated block particle filter}, currently the most powerful algorithm available in the \texttt{spatPomp} R package.

%  \vspace{2mm}

%  \item Bonus question: How do we know if our model is statistically adequate, or needs more work?

@@

\begin{frame}{Practical inference using IBPF}
  \begin{enumerate}
  \item Monte Carlo adjusted profile likelihood \citep{ionides17profile} obtains confidence intervals that accommodate Monte Carlo error.

  \item Comparing the log-likelihood with an autoregressive model (or other simple statistical model) provides a check of model fit.

  \item Comparing the block log-likelihood against the benchmark provides insight into problematic units.

    \item Comparing the conditional log-likelihood for each observation against the benchmark helps to identify outliers.

  \end{enumerate}

@@

\begin{frame}{Filtering $U$ units of a coupled measles SEIR model}

\begin{center}
\includegraphics[width=10cm]{mscale_loglik_plot-1.pdf}

\vspace{-4mm}

Simulated data using a gravity model with geography, demography and transmssion parameters corresponding to UK pre-vaccination measles (Ionides et al, {JASA}, 2023).

%\end{center}
